Dynamics of Laterally Propagating Flames in X-ray Bursts

### 2019-10-14 xrb/paper.tex
start of a table
add some more diffusion stuff

@@

Figure~\ref{fig:10_10_overview} shows the temperature, energy
generation rate, and $w$ component of the velocity (the out-of-plane
velocity induced by the Coriolis force).  This latter field
illustrates the hurricane effect set up by the laterally spreading
burning front.  In the energy generation rate plot, we see that the
burning is mostly concentrated toward the bottom of the layer, as
expected since the density is greatest there.  We see that the peak of
the burning has moved off of the symmetry axis, demonstrating that the
burning front is propagating to the right.  In the temperature plot,
we see the effect of our refinement criteria focusing only on the
atmosphere where we are most dense, with an artificial drop in the
temperature at the refinement boundary likely due to the thermal
diffusion. \MarginPar{Remind the reader what this was/where they should be looking in the plot to see this temperature drop} As we'll see when the lower resolution case, we do not
believe that this affects the results.

@@

Our default resolution puts $\sim 80$ zones vertically in the
``cool'' \MarginPar{double check} model atmosphere height.  To
understand the effects of resolution, we also performed a run with one
fewer level, giving a $20~\mbox{cm}$ resolution overall (this is our
10/10-lores run).  Figure~\ref{fig:10_10_lowres} shows the fields at
20~ms.  The structure is largely the same as the 10/10 run, with
largely the same flame shape and position, and the same structure in
the energy generation rate.  Since we do not have a jump in refinement
right below the atmosphere, we don't see the strong diffusive effect
there, but we do see some cooling in the \isot{Ni}{56} region.  This
is likely a resolution effect, again due to the strong gradient in
temperature at the base of the atmosphere.

@@

Show diffusion test problem and convergence.

\begin{figure}[t]
\centering
\plotone{diffusion_temp_amr}
\caption{\label{fig:diffusion} blah}
\end{figure}

>>>>

The initial model is created on a uniform grid at the resolution
corresponding to the finest level of refinement.  At regions of the
atmosphere that are not refined to the finest level, we interpolate
density, pressure, and composition on the grid and then obtain the
temperature from the EOS.  Because of the strong degeneracy at the
high densities at the bottom of the domain, the numerical error in the
interpolation can create a temperature jump there.\MarginPar{discuss better}

@@

Figure~\ref{fig:10_10_overview} shows the temperature, energy
generation rate, and $w$ component of the velocity (the out-of-plane
velocity induced by the Coriolis force).  This latter field
illustrates the hurricane effect set up by the laterally spreading
burning front.  In the energy generation rate plot, we see that the
burning is mostly concentrated toward the bottom of the layer, as
expected since the density is greatest there.  We see that the peak of
the burning has moved off of the symmetry axis, demonstrating that the
burning front is propagating to the right.  In the temperature plot,
we see the effect of our refinement criteria focusing only on the
atmosphere where we are most dense, with an artificial drop in the
temperature at the refinement boundary due to the interpolation
procedure of our initial model which focused on pressure and density
rather than temperature. \MarginPar{Remind the reader what this
  was/where they should be looking in the plot to see this temperature
  drop} As we'll see when the lower resolution case, we do not believe
that this affects the results.

@@

Our default resolution puts $\sim 80$ zones vertically in the
``cool'' \MarginPar{double check} model atmosphere height.  To
understand the effects of resolution, we also performed a run with one
fewer level, giving a $20~\mbox{cm}$ resolution overall (this is our
10/10-lores run).  Figure~\ref{fig:10_10_lowres} shows the fields at
20~ms.  The structure is largely the same as the 10/10 run, with
largely the same flame shape and position, and the same structure in
the energy generation rate.  Since we do not have a jump in refinement
right below the atmosphere, we don't see the temperature feature from
the initial model mapping there, but we do see some cooling in the
\isot{Ni}{56} region.  This is likely a resolution effect, again due
to the strong gradient in temperature at the base of the atmosphere.

@@

\begin{deluxetable}{rL}
	\tablecaption{\label{table:diffusion} Convergence of diffusion test problem.}
	\tablehead{\colhead{base resolution} & \colhead{L-inf error}}
	\startdata
\cutinhead{no refinement}
	32  & 5.995\times 10^{-3} \\
        64  & 1.477\times 10^{-3} \\
       128  & 3.664\times 10^{-4} \\
       256  & 9.139\times 10^{-5} \\
\cutinhead{one level of refinement}
        32  & 1.480\times 10^{-3} \\
        64  & 3.685\times 10^{-4} \\
       128  & 9.406\times 10^{-5} \\
       256  & 2.446\times 10^{-5} \\
	\enddata
	%
\end{deluxetable}

Table~\ref{table:diffusion} shows the L-inf error against the analytic
solution for the diffusion test problem.  The tests were run in two
fashions: no AMR, and AMR with one level of refinement (a jump of
$2\times$).  In both cases we see second-order convergence of the
error.  Figure~\ref{fig:diffusion} shows the temperature at the end of
the simulation of the $64\times 128$ base grid plus one level of
refinement simulation, with the grids shown to illustrate where the
refinement jump is.

\begin{figure}[t]
\centering
\plotone{diffusion_temp_amr}
\caption{\label{fig:diffusion} Temperature for the diffusion test problem at $10^{-3}~\mbox{s}$
for a diffusion test with a $64\times 128$ zone base grid and one level of refinement.}
\end{figure}
